```{r}
library(tidyverse)
```

```{r}
data <- read_csv("IEA-EV-data.csv")
```
sales$Country[sales$Country=="USA"]<-"United States of America"
```{r}
sales <- data %>%
  filter(region != "World") %>%
  filter(region != "Europe") %>%
  filter(region != "Other Europe") %>%
  filter(region != "Rest of the world") %>%
  pivot_wider(names_from = parameter, values_from = value) %>%
  select(-c("Electricity demand", "Oil displacement Mbd", "Oil displacement Mlge"))

sales$region[sales$region=="USA"]<-"United States of America "

sales_n <- sales %>%
  select(-c(category, mode, powertrain, unit)) %>%
  group_by(year, region) %>%
  summarise(sales = sum(`EV sales`, na.rm = TRUE),
            charingPoints = sum(`EV sales`, na.rm = TRUE),
            stock = sum(`EV stock`, na.rm = TRUE),
            stockShare = sum(`EV stock share`, na.rm = TRUE),
            salesShare = sum(`EV sales share`, na.rm = TRUE))

write.csv(sales_n,file='/Users/lukebonso/Desktop/total_ts.csv', row.names=FALSE)

```

```{r}
sales_ts <- data %>%
  filter(region != "World") %>%
  filter(region != "Europe") %>%
  filter(region != "Other Europe") %>%
  filter(region != "Rest of the world") %>%
  filter(parameter == "EV sales") %>%
  select(year, region, value) %>%
  filter(year <= 2020) %>%
  filter(region %in% c("Australia", " USA", "China", "Denmark", "United Kingdom", "Germany",
                       "Korea", "France", "Japan", "Sweden")) %>%
  group_by(region, year) %>%
  summarise(sales = sum(value))

```

```{r}
write.csv(sales_ts,file='/Users/lukebonso/Desktop/sales_ts.csv', row.names=FALSE)
```

```{r}
stock_ts <- data %>%
  filter(region != "World") %>%
  filter(region != "Europe") %>%
  filter(region != "Other Europe") %>%
  filter(region != "Rest of the world") %>%
  filter(parameter == "EV stock") %>%
  select(year, region, value) %>%
  filter(year <= 2020) %>%
  filter(region %in% c("Australia", " USA", "China", "Denmark", "United Kingdom", "Germany",
                       "Korea", "France", "Japan", "Sweden")) %>%
  group_by(region, year) %>%
  summarise(value = sum(value))

sales$region[sales_ts$region=="USA"]<-"United States of America "
```

```{r}
write.csv(stock_ts,file='/Users/lukebonso/Desktop/stock_ts.csv', row.names=FALSE)
```

```{r}
charging_points <- data %>%
  filter(region != "World") %>%
  filter(region != "Europe") %>%
  filter(region != "Other Europe") %>%
  filter(region != "Rest of the world") %>%
  filter(parameter == "EV charging points") %>%
  select(year, region, value) %>%
  filter(year <= 2020) %>%
  filter(region %in% c("Australia", " USA", "China", "Denmark", "United Kingdom", "Germany",
                       "Korea", "France", "Japan", "Sweden")) %>%
  group_by(region, year) %>%
  summarise(charging_points = sum(value))
```

```{r}
ts_sales_point <- charging_points %>%
  full_join(sales_ts)

ts_sales_point[is.na(ts_sales_point)] <- 0

write.csv(ts_sales_point,file='/Users/lukebonso/Desktop/ts_s_cp.csv', row.names=FALSE)
```

```{r}
types <- data %>%
  filter(region != "World") %>%
  filter(region != "Europe") %>%
  filter(region != "Other Europe") %>%
  filter(region != "Rest of the world") %>%
  filter(parameter == "EV stock") %>%
  filter(mode == "Cars") %>%
  select(year, region, powertrain, value) %>%
  filter(year <= 2020) %>%
  filter(region %in% c("Australia", " USA", "China", "Denmark", "United Kingdom", "Germany",
                       "Korea", "France", "Japan", "Sweden")) %>%
  group_by(region, year, powertrain) %>%
  summarise(value = sum(value))
```

```{r}
write.csv(types,file='/Users/lukebonso/Desktop/types.csv', row.names=FALSE)
```

